Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a sun-like pair

### 2017-06-09 paper/ms.tex
Add software ack.
Remove todo.
No also.
fix title grammar

\title{
  Kronos \& Krios:
  Evidence for accretion of massive, rocky planetary system in a sun-like pair
}

@@

The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
confirming that they are truly comoving.
Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
can compare differences between the inferred 6D phase-space coordinates of the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix.
%TODO: what is assumed for uncertanties in RV?
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}
(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot = (10,\,244,\,7.17)~\kms$.
% TODO: APW (\citealt{bovy, etc.}).
\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
The differences in positions and velocities are consistent with zero.

@@

%TODO: augment this paragraph
% - more geochemical study references
We stress that while the calculation carried out is useful in
order-of-magnitude sense, further investigation of each of the simplifying
assumptions made is warranted.
In addition, the composition of bulk Earth also has some uncertainties.
For example, the reported bulk Earth concentration of the siderphile element
\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
While the latter value from \citealt{mcdonough2001composition} has been used in
our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
to an even closer agreement.
Given these limitations, the level of agreement for the refractory {\it and}
\elem{Li} for \bizarreone\ is remarkable.

@@

\software{
  %The data and code used in this project is available from
  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
  %software license.
  This research utilized:
  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
  \texttt{IPython} (\citealt{Perez:2007}),
  \texttt{matplotlib} (\citealt{Hunter:2007}),
  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
  and \texttt{pandas} (\citealt{pandas}).}

>>>>

\title{
  Kronos \& Krios:
  Evidence for accretion of a massive, rocky planetary system in a sun-like pair
}

@@

The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
confirming that they are truly comoving.
Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
can compare differences between the inferred 6D phase-space coordinates of the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix.
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}
(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot = (10,\,244,\,7.17)~\kms$.
% TODO: APW (\citealt{bovy, etc.}).
\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
The differences in positions and velocities are consistent with zero.

@@

%TODO: augment this paragraph
% - more geochemical study references
We stress that while the calculation carried out is useful in
order-of-magnitude sense, further investigation of each of the simplifying
assumptions made is warranted.
In addition, the composition of bulk Earth has some uncertainties.
For example, the reported bulk Earth concentration of the siderphile element
\elem{Mn}, varies from $800$ to $1700$~ppm (\citealt{1998psc..book.....L}).
While the latter value from \citealt{mcdonough2001composition} has been used in
our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
to an even closer agreement.
Given these limitations, the level of agreement for the refractory {\it and}
\elem{Li} for \bizarreone\ is remarkable.

@@

\software{
  %The data and code used in this project is available from
  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
  %software license.
  This research utilized:
  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
  \texttt{emcee} (\citealt{2013PASP..125..306F}),
  \texttt{IPython} (\citealt{Perez:2007}),
  \texttt{matplotlib} (\citealt{Hunter:2007}),
  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
  and \texttt{pandas} (\citealt{pandas}).}
